Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-07-29 analysis/paper/shceof.Rmd
Agrega más intro

\textcolor{red}{Agregar parráfo que introduzca el problema del estudio de la ciriculación extra-tropical en SH, su variaiblidad y sus cambios. Quizás algo también de los impactos. También algo habría que decir de la primavera, ya que solo nos concentrmaos en esa estación}

@@

@@

Another approach to characterising the Southern Hemisphere circulation is by using Empirical Orthogonal Functions (EOF, also known as Principal Component Analysis).
Within the EOF framework, the Southern Annular Mode (SAM) appears as the leading mode of variability of the tropospheric Southern Hemisphere circulation [@fogt2020] followed by the two Pacific--South American Patterns (PSA) [@mo2001].
The SAM represents a relatively zonally symmetric pattern of alternating low pressures in polar latitude and a ring of high pressures in high latitudes with an embedded wave 3 pattern that is more prominent in the Pacific sector.
The PSA1 and PSA2 describe the two out-of-phase sides of a meridionally propagating wave train that originates in the Eastern equatorial Pacific and travels towards the South Atlantic following a great-circle arch along the Antarctic Peninsula.
These patterns are derived by applying EOF to temporal anomalies, but @raphael2003 applied EOF methods specifically to zonal anomalies.

>>>>

@@

For example, @raphael2007 suggests that variability in the planetary wave 3 projected onto its climatological location is associated with Antarctic sea ice concentration anomalies. @irving2015 showed that planetary wave amplitude in general is associated sea ice concentration, as well as temperature and precipitation anomalies. Another characteristic of the zonally asymmetric circulation are the Pacific--South American Patterns [@mo2001], which are associated with precipitation anomalies in South America.

Some of these patterns of variability appear to have experienced secular changes. @raphael2003 found that the amplitude of the zonal wave 1 experienced a large increase and that the zonal wave 3 experienced changes in its annual cycle between 1958 and 1996.

@@

The fourier technique can be generalised to integrate all planetary wave intensity irregardless of wave number by computing the wave envelope as done by @irving2015. This makes it possible to represent planetary waves with different amplitude at different longitudes, but it removes all information about phase and wave number.

Another approach to characterising the Southern Hemisphere circulation is by using Empirical Orthogonal Functions (EOF, also known as Principal Component Analysis).
Within the EOF framework, the Southern Annular Mode (SAM) appears as the leading mode of variability of the tropospheric Southern Hemisphere circulation [@fogt2020] followed by the two PSA [@mo2001].
The SAM represents a relatively zonally symmetric pattern of alternating low pressures in polar latitude and a ring of high pressures in high latitudes with an embedded wave 3 pattern that is more prominent in the Pacific sector.
The PSA1 and PSA2 describe the two out-of-phase sides of a meridionally propagating wave train that originates in the Eastern equatorial Pacific and travels towards the South Atlantic following a great-circle arch along the Antarctic Peninsula.
These patterns are derived by applying EOF to temporal anomalies, but @raphael2003 applied EOF methods specifically to zonal anomalies.
